Assignment 2: Interpreting Quantitative Findings

### 2023-06-15 paper.tex
speciale edits

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Assignment 2: Interpreting Quantitative Findings},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{lastpage}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[CO,CE]{Page \thepage\ of \pageref{LastPage}}
\usepackage{floatrow}
\floatsetup[figure]{capposition=top}
\floatsetup[table]{capposition=top}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Assignment 2: Interpreting Quantitative Findings}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{\hfill\break
University of Glasgow\\
\strut \\
Student ID: 2819052\\
Course: Quantitative Methods\\
Number of words: 1076}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

@@

\setcounter{tocdepth}{2}
\tableofcontents

@@

@@

In 1998, the Good Friday/Belfast Agreement was signed and later
validated by the voters, and this agreement marked a new era of hope
towards peace, equality, and inclusion in Northern Ireland
(\protect\hyperlink{ref-galligan2013gender}{Galligan 2013}). The main
focus on the agreement and referendum was obviously to stop the violent
conflict and seek peace, but one part of the agreement also emphasized
an equality agenda (\protect\hyperlink{ref-Hayward2021}{Hayward 2021}).
Thus, the agreement also marked the first Northern Irish formal
recognition of women's rights to political inclusion
(\protect\hyperlink{ref-galligan2013gender}{Galligan 2013}). However, a
formal recognition does not necessarily imply that gender equality
trickles down into social norms and practices. Therefore, this report
examines the contemporary state of women's equality in Northern Ireland.

Perhaps, the most central concept within gender equality is the
\emph{gender pay gap}. Disparities in income is an important indicator
for gender equality, because it has social, economic, and physiological
consequences (\protect\hyperlink{ref-bishu2017gender}{Bishu and Alkadry
2017}). Research on this area have identified several factors that seems
to influence a gender pay gap. One such factor can be inequality in
access to workplace authority, where women are denied manager or
supervisor position although there were equally qualified
(\protect\hyperlink{ref-bishu2017gender}{Bishu and Alkadry 2017}). Other
factors can be discrimination in hiring or promotion processes, but also
lack of gender representation can avoid minorities to even apply for a
job or promotion (\protect\hyperlink{ref-bishu2017gender}{Bishu and
Alkadry 2017}).

In order to examine the current gender equality in Northern Ireland, we
therefore focus on the gender pay gap in Northern Ireland. We ask the
following research question: \emph{Does gender affect income in
contemporary Northern Ireland?} We employ a deductive approach, where we
first formulate a hypothesis and subsequently examine it empirically
(\protect\hyperlink{ref-bryman2016social}{Bryman 2016, 33}). Therefore,
our analysis consider the following null hypothesis (H\textsubscript{0})
and alternative hypothesis (H\textsubscript{A}):

\begin{itemize}
\tightlist
\item
  H\textsubscript{0}: Being a woman or man does not affect your income.
\item
  H\textsubscript{A}: Being a woman rather than a man affects a lower
  income.
\end{itemize}

The causal relationship that we examine is thus a negative relationship.
Although, we call this relationship causal, it is important to clarify
that I do not imply that there is anything biological or deterministic
that reduce women's income in general. Rather, the causal link is
interpreted as a result of the societal discriminatory practices
explained in the previous paragraph. To make a convincing inquiry of
this causal relationship, we must also control for a number of other
factor related to income and gender. This is important to make sure that
our analysis do not simply show a spurious correlation as it could in
fact be another factor that influences both gender and income. These
control variables are introduced in the Data and Methods-section.

\hypertarget{data-and-method}{%
\section{Data and method}\label{data-and-method}}

The research design of this analysis is a cross-sectional design
(\protect\hyperlink{ref-bryman2016social}{Bryman 2016, 53}). This means
that the data for analysis is collected at a single point in time and
consists of a sample of respondents from which we seek to infer to a
general population of Northern Ireland
(\protect\hyperlink{ref-field2012discovering}{Field, Miles, and Field
2012, 36}). This section describes this sample and how the data was
collected, and then subsequently the operationalized variables to
examine our research hypothesis are described.

\hypertarget{sample-and-data-collection}{%
\subsection{Sample and Data
Collection}\label{sample-and-data-collection}}

Our sample for the analysis consists of data from Northern Ireland Life
and Times Survey (NILT). The data have been collected every year since
1998, but this analysis uses the survey from 2012
(\protect\hyperlink{ref-ark_2012}{ARK 2012}). The respondents for the
NILT survey was chosen from a systematic random sample of addresses.
From this sample of 2126 addresses, 1204 questionnaires were fully
completed using partly face-to-face- and self-completion questionnaires
(\protect\hyperlink{ref-ark_2012}{ARK 2012}). Our sample of analysis is
further reduced as not all respondents have answered our variables of
interest, and we are therefore not able to include those respondents in
our analysis. In the tables below, we present descriptive statistics for
our variables of interest in both the full NILT sample and our sample of
analysis. The first tables shows the categorical variables, where a
frequency distribution are shown
(\protect\hyperlink{ref-fogarty2018quantitative}{Fogarty 2018, 88}). The
second table shows the numerical variables, where we have calculated the
mean and standard deviation
(\protect\hyperlink{ref-fogarty2018quantitative}{Fogarty 2018, 95}).

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\author{}
\date{\vspace{-2.5em}}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{dcolumn}
\usepackage{lastpage}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{wrapfig}
\setlength\parindent{24pt}
\usepackage[explicit]{titlesec}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\pagestyle{fancy}
\fancyhead{}
\setcounter{page}{0}
\fancyfoot[CO,CE]{Page \thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\usepackage{floatrow}
\floatsetup[figure]{capposition=top}
\floatsetup[table]{capposition=top}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\begin{document}

\thispagestyle{empty}

\vspace{2cm}

\includegraphics[]{images/ku_logo_no_txt.png}

\vspace{2cm}

\Large

\textbf{University of Copenhagen}

\textbf{Department of Sociology}

\begin{centering}

\vspace{3cm}

\Large

\doublespacing
\textbf{MORE THAN LIKES: HOW NEWS CONTENT INFLUENCES AUDIENCE ENGAGEMENT ON SOCIAL MEDIA}

\vspace{1 cm}

\normalsize
\singlespacing
A Master Thesis by

\vspace{0.5 cm}

\Large

\textbf{Tobias Priesholm Gårdhus}

\normalsize
\vspace{0.5 cm}

\&

\vspace{0.5 cm}
\Large
\textbf{Mads Lang Sørensen}

\normalsize
\vspace{1.5 cm}

Supervisor: Christian Borch

Number of characters: 217,328

Date: 31\textsuperscript{th} of May 2023

\vspace{1.5 cm}

\end{centering}
\normalsize

\newpage

\onehalfspacing

\vspace*{2cm}

\begin{center}\includegraphics[width=0.8\linewidth]{images/midjourney_gen} \end{center}
\begin{center}
An image generated by Midjourney's image generation model using the prompt:

\noindent
\emph{“A renaissance painting of people arguing over the content of a tabloid newspaper”.}
\end{center}

@@

\hypertarget{abstract}{%
\subsection*{Abstract}\label{abstract}}
\addcontentsline{toc}{subsection}{Abstract}

This study investigates how the content of news articles influences
audience engagement on social media. Addressing research gaps in
previous studies, which often rely on limited or biased samples and
narrow definitions of audience engagement, this study utilizes machine
learning and natural language processing techniques to analyze a
comprehensive dataset of news content shared on Facebook over a span of
nearly two years. By collaborating with Ekstra Bladet, the largest
Danish tabloid media, we are able to examine multiple different
dimensions of audience engagement encompassing information selection,
emotional responses, sharing, and conversations. Through an empirical
analysis of the influence of 11 news content characteristics on eight
audience engagement outcomes, the analysis can be summarized in three
main findings. First of all, news content characterized by
unexpectedness and soft news increases individualistic behaviors, such
as clicking on articles, while impact and hard news increase social
behaviors, such as sharing and having conversations. Secondly, the
emotional framing of news content elicits similar emotional responses
among the audience, with positivity and negativity prompting more
recognizing and offensive language, respectively, in the comment
section. Thirdly, news content related to timeliness and proximity shows
limited effects on audience engagement. These findings highlight the
multidimensional nature of audience engagement, underscoring that there
is no universal influence of news content on audience engagement on
social media.

\hypertarget{declaration-of-responsibilities}{%
\subsection*{Declaration of
Responsibilities}\label{declaration-of-responsibilities}}
\addcontentsline{toc}{subsection}{Declaration of Responsibilities}

Tobias Priesholm Gårdhus: 1, 2.1, 2.3, 2.5, 2.6, 3.2, 3.4, 3.6, 4.1,
4.3, 4.5, 5.1, 5.3, 6

\noindent Mads Lang Sørensen: 1, 2.2, 2.4, 2.6, 3.1, 3.3, 3.5, 3.6, 4,2,
4.4, 4.5, 5.2, 5.4, 6

\hypertarget{declaration-of-third-party-collaboration}{%
\subsection*{Declaration of Third-party
Collaboration}\label{declaration-of-third-party-collaboration}}
\addcontentsline{toc}{subsection}{Declaration of Third-party
Collaboration}

As part of the study, the authors collaborated with a third-party,
Ekstra Bladet, for data availability. However, no conflict of interest
has arisen throughout the process.

@@

\singlespacing

\setcounter{tocdepth}{3}
\tableofcontents

\onehalfspacing

@@

\hypertarget{background}{%
\subsection{Background}\label{background}}

News media have always played a central role in a well-functioning
democracy. The democratic role of media is to serve as an independent
and objective reporter of the truth (Herman \& Chomsky 1988:55). A
common metaphor is that the media represents the watchdog of democracy
by exposing the elite and those in power (Kovach \& Rosenstiel
2014:160ff). Furthermore, news media has an important obligation to
inform and facilitate public discussion about important societal topics
(Aalberg \& Curran 2012:3; Habermas 1999). However, in recent years, the
role of the media has been questioned due to new digital technologies
and possibilities. Perhaps the most significant consequence is the
changing relationship between media and their audiences (Richardson \&
Stanyer 2011; Livingstone 2016:2).

Increasingly, many people turn to social media as their preferred
platform for reading and engaging with news content. For the first time
in 2022, Danish audiences spent more time on social media than on
traditional print, radio, and broadcast media (DR Medieforskning
2022:14). Social media allow users to engage with news content in far
more ways than when it was distributed through newspapers, radio, or TV
(Jenkins et al.~2013:6ff). Furthermore, media organizations, editors,
and journalists no longer hold the monopoly of media production and
dissemination; anyone can participate in debates and act as a reporter
or commentator (Deuze 2005:451). In many ways, the audiences play a more
active role in the relationship with the media. Unlike the days of
opinion letters and face-to-face conversations, social media and website
analytics allow audience feedback to be tracked and analyzed directly
within the newsroom (Richardson \& Stanyer 2011; Christin 2018;
Ferrer-Conill \& Tandoc 2018:436).

The audience engagement can also be seen as a part of a digital public
sphere, where individuals discuss news content and exchange arguments.
However, this deliberative potential may not always be realized, and
some argue that the audience engagement pollutes the public debate more
than they benefit it (Papacharissi 2002). As a consequence, media
organizations have been shutting down the comment sections on their own
websites, and instead used social media platforms such as Twitter and
Facebook for social interactions (Reimer et al.~2021:4). Recently,
multiple Danish media have taken a step further and decided to remove
the possibility to comment on shared articles on their Facebook pages,
due to the number of uncivil comments. However, this decision is not
without consequences. In addition to hindering the possibility of
deliberation, these media sites' posts also reach a smaller audience --
reducing the impact of the news content (Albrecht 2022). Rather than
completely shutting down conversations around news content, it might be
more sustainable to examine what drives different kinds of audience
engagement. Following these considerations, there are democratic,
societal, and academic reasons to better understand audience engagement
with news content on social media.

\hypertarget{news-content-and-audience-engagement}{%
\subsection{News Content and Audience
Engagement}\label{news-content-and-audience-engagement}}

It is far from all kinds of news content that audiences engage with on
social media. While a minority of posts receive thousands or even
millions of clicks, likes, shares, comments, or other types of
engagements, most posts only receive a few interactions. Understanding
what drives audiences to engage or abstain from engaging with news
content on social media is important. On the one hand, audience
engagement is an important part of opinion-making, which is a central
part of a democratic society (Steensen, Ferrer-Conill \& Peters
2020:1665). On the other hand, audience engagement may also affect the
production of media content by determining what content is popular and
thus also what content is most profitable for the media (Martin 2019).
The concept of audience engagement has been defined in many different
ways, but generally it refers to an active or intentional orientation
towards the news content (Broersma 2019:1). In this study, we argue that
audience engagement should be understood as a multifaceted phenomenon
encompassing different dimensions related to information selection,
emotional reactions, sharing of content, and not least having
conversations about content.

Research has identified several factors that influence audience
engagement on social media. In a review by Kümpel et al.~(2015) three
types of factors are identified: users, content, and social networks.
This distinction is reminiscent of the classical work on media and
audiences by Katz \& Lazarsfeld (1955), where they identify five
intervening variables between media and audiences: exposure, medium,
content, predispositions, and interpersonal relations. In this study, we
will focus only on how one of these variables influence audience
engagement: the news content itself.

To determine the characteristics of news content that might influence
audience engagement, many studies have used the idea of news values.
Taxonomies of different news values have traditionally been used as a
journalistic guideline of a story's newsworthiness, but it has also been
adapted to explain how audiences evaluate the relevance of content
(Harcup \& O'Neill 2001:7; Eilders 2006). From the original formulation
by Galtung \& Ruge (1965) to contemporary reformulations of news value
theory, the categories of news values have varied greatly, but they
often include news content characteristics such as timeliness,
unexpectedness, proximity, negativity, and positivity.

\hypertarget{empirical-gap}{%
\subsection{Empirical Gap}\label{empirical-gap}}

The question of how news content influences audience engagement on
social media has been approached in various fields within both social
sciences, humanities, and natural sciences (Kümpel et al.~2015:8).
Although a lot of research has been conducted within this field, we
argue that specifically two empirical gaps remain.

First and foremost, most studies have relied on smaller samples of the
shared news content. Articles, posts, and comments have mainly been
sampled based on different analytical heuristics (e.g., selection for
qualitative analysis) or technical limitations (e.g., the
restrictiveness of social media platform's data access), while few
studies have computationally analyzed a full population of posts and
comments over an extended period. Furthermore, some studies have only
studied the news content that is most engaged with, but not what is less
engaged with (Kümpel et al.~2015:8-9). This limitation often stems from
data constraints, where empirical analyses are restricted to the top
news articles and their engagement. This approach is particularly
problematic, since it only examines what is successful and not what is
not successful. To better determine the factors driving audience
engagement, the complete population of news articles should be included
in the analysis.

A second limitation of previous research is the predominantly simple and
narrow conceptualization and measurement of audience engagement. Often,
audience engagement is aggregated into basic popularity cues, such as
the number of likes or shares (Steensen et al.~2020:1663). However,
audience engagement is a multifaceted phenomenon that can be both
behavioral and felt (Steensen et al.~2020:1665). While the felt
engagement is difficult to capture with quantitative metrics, digital
traces enable us to construct different measurements for behavior. Even
if we only consider behavioral engagement, there might be a significant
difference between a user simply clicking the link, liking a post,
sharing it to their own feed or even discussing the content in a comment
thread. While quantitative popularity cues are often the focus for media
organizations due to their connection to ad revenue, audience engagement
may also contain undesired behaviors such as incivilities in the comment
sections (Martin 2019:21; Su et al.~2018; Chen et al.~2020). To our
knowledge, no previous empirical studies have examined how different
news content might drive different dimensions of audience engagement.

\hypertarget{research-question}{%
\subsection{Research Question}\label{research-question}}

This study seeks to close the empirical gaps described in the previous
section. Overall, we seek to answer the following research question:

\begin{quote}
\emph{How does the content of news articles influence audience
engagement on social media?}
\end{quote}

\hypertarget{analytical-contribution}{%
\subsection{Analytical Contribution}\label{analytical-contribution}}

This study aims to bridge the empirical gaps in previous research on the
relation between audience engagement and news content by constructing a
unique and comprehensive dataset. The creation of our dataset and
analysis is made possible by collaborating with Ekstra Bladet - the
largest tabloid media in Denmark. Approximately one million people visit
their website every day. Ekstra Bladet also publish a printed newspaper
and share their articles on various social media such as their Facebook
page with over 400,000 followers. While tabloid in style, they cover all
areas of society and journalistic practice, ranging from celebrity
gossip to award-winning investigative journalism (Journalistforbundet
2023).

By collaborating with Ekstra Bladet, we can construct a more complete
dataset that overcomes the empirical limitations of previous research.
First of all, we are able to include all articles shared on Ekstra
Bladet's Facebook page for almost two years in our analysis. This allows
us to analyze a complete population of articles for a longer period --
rather than relying on a smaller sample that could contain biases or
lack representativeness. To be able to construct measures of audience
engagement and news content characteristics for this extensive dataset,
we apply computational methods, including machine learning and natural
language processing techniques, rather than the manual hand-labelling
that most previous studied have relied upon. Secondly, we examine social
media engagement by a multitude of different manifestations instead of
only relying on a simple and narrow measurement. Our access to Ekstra
Bladet's Facebook page allows us to retrieve detailed post and comment
data from Facebook, and therefore collect a multitude of features not
otherwise available. Instead of only retrieving common popularity cues
such as the number of likes, we are also able to collect text content
and structure of the comment section, and metrics that are only visible
to the Facebook page-owner i.e., number of clicks on the shared link. In
this way, our study extends and improves the previous empirical
foundation by both including a more complete population of news content
and a more comprehensive understanding of audience engagement on social
media.

\hypertarget{data-and-methods}{%
\subsection{Data and Methods}\label{data-and-methods}}

Our dataset is constructed by combining two different data sources. The
first dataset comes from Ekstra Bladet's database and consists of
article content and aggregated user behavior on their website. The
second dataset is collected from Facebook and consists of all posts made
by Ekstra Bladet's Facebook page, along with information about the
engagement for the posts and their comment sections. Our unit of
observation is therefore the shared posts for which we construct the
features of news content characteristics and audience engagement on
Facebook.

The dataset spans over almost two years from the 28\textsuperscript{th}
of February 2021 to the 1\textsuperscript{st} of January 2023 and
contains 18,350 Facebook posts. In aggregate metrics, our measures of
audience engagement encompass approximately 5.5 million comments, 7
million likes, and 230 million clicks on links to the shared articles.
As audience engagement is defined as a multifaceted phenomenon, we
operationalize its various dimensions on social media into eight
different outcomes related to information selection, emotional
responses, sharing, and conversations about news content. Similarly, we
define 11 news content characteristics mainly derived from news value
theory. Utilizing multiple linear regression, we analyze the influence
of these 11 news content characteristics on each of the eight
measurements of audience engagement on social media.

\hypertarget{reading-guide}{%
\subsection{Reading Guide}\label{reading-guide}}

The thesis is structured as follows. Section 2 (Theoretical Background)
delves into the existing body of knowledge surrounding audience
engagement and news content. We review relevant previous studies,
theories, and frameworks that inform our research, and highlight the two
research gaps that our study aims to address. Section 3 (Data and
Methods) describes the research design, data collection,
operationalization of audience engagement and news content, and the
analytical methods employed. The last part of Section 3 also outlines
important background information about our case of study, Ekstra Bladet.
Section 4 (Analysis) presents the results of our empirical analysis
structured in four dimensions of audience engagement on social media:
information selection, emotional responses, sharing, and conversations.
Concluding on Section 4, we present three main findings across the
outcomes of audience engagement on social media. In Section 5
(Discussion), we discuss our empirical research in the light of the
societal and theoretical implications, the reliability and validity, as
well as the generalization of our findings to other cases. Section 6
(Conclusion) summarizes the key findings of the study and highlights
limitations of the study along with suggestions for further research in
the field.

\hypertarget{theoretical-background}{%
\section{Theoretical Background}\label{theoretical-background}}

In this section, we review and discuss the theoretical background and
previous literature related to our study. The research subject of our
study has been approached from multiple different disciplines within
both the humanities, natural sciences, and social sciences. In the
following theoretical and empirical review, we include related research
across different scientific approaches, while our own approach is mainly
sociological.

The first part (2.1) describes how theories of the relationship between
media and audiences have developed until today, and how they are
relevant to our study. The second part (2.2) focuses on the consequences
of social media and digital technologies and relates this digital
evolution to the relationship between media and audiences. These two
first parts serve as background information that places our study in a
broader theoretical context. Subsequently, the third part (2.3)
elaborates on the concept of audience engagement on social media and
presents findings from previous studies. In the fourth part (2.4), we
consider news content might be understood, and what characteristics of
news content might influence audience engagement. In the final part
(2.5), we discuss two empirical limitations within previous research,
which shows the relevance of our current study.

\hypertarget{media-and-audiences}{%
\subsection{Media and Audiences}\label{media-and-audiences}}

The relationship between media and audiences is an essential topic
within media and communications research (Livingstone 2016:1). The
concept of an audience has been central since the first formulations of
media theories, and in the current digital age, the concept of audiences
is more prevalent than ever (Livingstone 2016:1-2). In this section, we
will describe the theoretical developments of the theories about media
and audiences, and finally discuss how the idea of audiences has become
central to contemporary debates in media studies.

\hypertarget{mass-media-and-passive-audiences}{%
\subsubsection{Mass Media and Passive
Audiences}\label{mass-media-and-passive-audiences}}

\noindent The early formulations of theories about media are closely
related to the emergence of mass media (Merrin 2014:95). The
popularization of broadcasting through radio and television gave rise to
the concept of a mass being stimulated with content by a single media
producer (Merrin 2014:94). Lippmann (1922) was one of the first to
describe the idea of a transmission model where media is sent from the
producer to the audience. He emphasized how mass media was shaping
public opinion by transmitting cognitive stereotypes to a mass of people
(Lippmann 1922). Consequently, he was quite critical of mass media, as
it carries the potential to manipulate rather than inform the public.
This critical perspective has been continued even more famously in the
works of Herman and Chomsky and their idea of manufacturing consent
(Herman \& Chomsky 1988), as well as in the works of Adorno and
Horkheimer on enlightenment as mass deception (Adorno \& Horkheimer
2002; Adorno 1991). In both of these approaches, the mass audience is
deceived, as the media present them with simplified or biased portrayals
of the world, promoting conformity rather than an informed and critical
consciousness (Adorno 1991:104).

The concept of a transmission model of media has also been developed
within a tradition that is less normative, adopting a more positivistic
approach. Prominently, the two mathematicians Shannon and Weaver (1949)
summarized the relationship between media and audiences in their
sender-message-receiver model. This theoretical model has a clear causal
relationship: a sender (e.g., the news media) transmits a message, which
is received by the audience and produces a specific effect. Similar to
Shannon and Weaver's model, Lasswell (2007) also described a
transmission model formulated as a chain of questions: who says what in
which channel to whom with what effect (Wanta \& Myslik 2019:59-60)?
These theoretical models have had a large impact on media studies, and
many studies have examined media effects of different kinds of content
and audiences, but always with an emphasis on a one-way, causal
direction from media producers to media consumers (Wanta \& Myslik
2019:59-60).

\hypertarget{the-idea-of-active-audiences}{%
\subsubsection{The Idea of Active
Audiences}\label{the-idea-of-active-audiences}}

\noindent Most contemporary research within media studies has moved away
from the notion of audiences as passive masses without any agency. In
the latter half of the 20th century, several different approaches
contested the previous understanding of audiences. Different theoretical
approaches have argued that audiences should be seen as being more
diverse and having more agency. Three of the most important approaches
that we will mention here are: 1) interpersonal relations by Katz \&
Lazarsfeld (1955), 2) the encoding-decoding model by Hall (1973), and 3)
Livingstone's (2005) concept of active audiences.

Katz and Lazarsfeld (1955) were among the first to challenge the
mass-communication-idea of audiences as a passive receiver. They
identify five different intervening variables affecting the relationship
between media and audiences: exposure level, medium type, media content,
audience predispositions, and interpersonal relations (Katz \&
Lazarsfeld 1955:20-25). Their work emphasizes the fifth variable,
interpersonal relations, since it gives a new kind of agency among the
audience members. Readers of a newspaper and viewers of a television
shows are not just separate individuals, but they have interpersonal
relationships through social networks and group norms, which mediates
the influence of the media (Katz and Lazarsfeld 1955:43-44). Katz and
Lazarsfeld also introduced the idea of a two-step flow of communication,
where opinion leaders -- people with especially significant
interpersonal influence -- distribute and mediate the flow of
information from media to the audiences (Katz \& Lazarsfeld 1955:32).

Another important contribution within media studies is the works of Hall
(1973). He argues that there can never be one single stimuli-effect of a
media message, because both the process of media production and media
reception are embedded in ideologies (Hall 1973:265). When journalists
and media workers produce content, it is encoded with different
knowledge and assumptions, and subsequently the media content is decoded
by the audience and reacted to according to their structural and
cultural position.

In more contemporary research, the idea of active audiences has also
been greatly emphasized by Livingstone (2006:9). She argues that
audiences are increasingly diversified and situated within specific
communities (Livingstone 2006:9-10). This perspective strongly
emphasizes that media messages are fully interpreted within communities,
and thus the approach has had a strong focus on ethnographic methods
(Livingstone \& Das 2013:1-2). In its most extreme formulation, there is
no inherited meaning in media content, and media content will have
completely different meanings for different communities (Philo et
al.~2015:464).

Although the approaches of Katz and Lazarsfeld, Hall, and Livingstone
are quite different in nature, they all share the common trait of
imagining an audience that has some kind of agency -- both towards media
producers and each other. To some extent, the theoretical approaches to
media and audiences can be placed on an axis of how much agency is
attributed to the audience, and how unified or fragmented the audience
is thought to be (Philo et al.~2015:464). While recognizing that these
underlying dynamics are a part of the subject, our study will have a
specific empirical focus on the relationship between the news content
and audience engagement.

\hypertarget{audiences-2.0}{%
\subsubsection{Audiences 2.0}\label{audiences-2.0}}

\noindent The idea of an audience is both a central pillar in media
theory and an essential part of everyday practices in newsrooms
(Livingstone 2016:1-2). Nevertheless, many researchers have started to
question the contemporary relevance of the concept of audiences. The
critique is mainly a consequence of the concept being firmly connected
to specific technological mediums: mass broadcasting media such as radio
and television (Livingstone 2016:2). Recently, mass broadcasting media
has been greatly challenged by digital media. Some argue that this
technological evolution also has deep consequences for previous media
theories - because they simply no longer fit the digital reality - to
such a degree that we need to develop a media studies 2.0 (Merrin 2014).
